Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-08-21 paper/amia.tex

KFP provides a framework by which any number of methods for data privacy can be carried out. For demonstration purposes we have implemented two plugins that use different techniques for data synthesis. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthezier offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

>>>>

KFP provides a framework by which any number of methods for data privacy can be carried out. For demonstration purposes we have implemented two plugins that use different techniques for data synthesis. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
